---
title: "halleyxlyn17.github.io"
---

About this site
Welcome to Xulin's Website!

Introduction:The GBD Study 2010 estimated the burden of diseases, injuries, and risk factors globally and for 21 regions for 1990 and 2010.

The dataset provides number of deaths and mortality rates for 187 countries, 21 regions, and globally by age group and sex, for 1970, 1980, 1990, 2000 and 2010. The other provides the probabilities of dying between the ages of 15 and 60 (45q15), the probabilities of dying between birth and age 5 (5q0), and mean ages of death for the same geographies and years, and by sex. 

```{r}
read.csv("/Users/halleyzhou/Documents/dataset.csv")
```

```{r}
library(shiny)
library(readr)

# Define UI
ui <- fluidPage(
  titlePanel("Scatterplot"),
  sidebarLayout(
    sidebarPanel(
      fileInput("file", "Choose CSV File",
                accept = c(".csv"))
    ),
    mainPanel(
      plotOutput("scatterplot")
    )
  )
)

# Define server logic
server <- function(input, output) {
  # Read the CSV file
  data <- reactive({
    req(input$file)
    read_csv(input$file$datapath)
  })

  output$scatterplot <- renderPlot({
    req(data())
    plot(data()$x, data()$y, main = "Scatterplot", xlab = "X", ylab = "Y")
  })
}

# Run the application
shinyApp(ui = ui, server = server)
```       

```{=html}
https://harleyxlyn17.shinyapps.io/halleysapp/
<iframe height="400" width="100%" frameborder="no" src="https://datasciencegenie.shinyapps.io/MyShinyApp/"> </iframe>
```

```{r}

# Install and load the png package

library(png)

# Read the PNG image
img <- readPNG("/Users/halleyzhou/Documents/WechatIMG302.jpg")
print(img)


```

