---
title: "halleyxlyn17.github.io"
---

About this site Welcome to Xulin's Website!

Economic gender inequality has long been a pervasive issue, manifesting in disparities in pay, job opportunities, and wealth accumulation between men and women. 

Despite progress in recent decades, these gaps continue to persist, albeit to a lesser extent than before. This dataset delves into the intricate landscape of economic gender inequality, exploring its dimensions.

```{r}
df = read.csv("/Users/halleyzhou/Documents/gendergapinaverage new.csv")
```
```{r}

# Load the png package
library(png)
# Define the path to the image file
image_path <- "/Users/halleyzhou/Documents/WechatIMG322.png"  # Replace with the path to your PNG file

# Load the PNG image
image <- readPNG(image_path)

# Plot the image
plot(1:2, type = "n", xlab = "", ylab = "", main = "")
# The rasterImage() function allows you to place the image on the plot
rasterImage(image, 1, 1, 2, 2)

```

```{r}
library(ggplot2)


data <- read.csv("/Users/halleyzhou/Documents/gendergapinaverage new.csv")


ggplot(data, aes(x=Year, y = Gender.wage.gap..)) +
  geom_point(color = "blue", size = 3) +
  labs(title = "Scatterplot", x = "Year", y = "Gender Wage Gap") +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 12),
    axis.line = element_line(color = "red"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank()
  )

```








Scatterplot App:

```{=html}
<iframe height = "400" width = "100%" src = "https://harleyxlyn17.shinyapps.io/halleysapp/"></iframe>
```

```{=html}
<iframe height = "400" width = "100%" src =
"https://harleyxlyn17.shinyapps.io/app_3/"></iframe>

```

```{=html}
<iframe height = "400" width = "100%" src =
"https://harleyxlyn17.shinyapps.io/app_2/"></iframe>